%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Bioinformatics Director} % Job title
    {Shenzhen Aegicare Technology Co., Ltd.} % Organization
    {Shenzhen, Guangdong, China} % Location
    {May 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the construction of a fully automated genetic disease detection platform, overseeing the entire process from technical solution design to practical application, ensuring standardization and efficiency of testing workflows}
        \item {Responsible for development of an integrated variant detection device, coordinating the team to complete technical challenges and product commercialization, enhancing the practicality and stability of detection equipment}
      \end{cvitems}
    }\\


%---------------------------------------------------------
  \cventry
    {Hematological Tumor Project Bioinformatics Team Leader} % Job title
    {Beijing Acorndx Biotechnology Co., Ltd.} % Organization
    {Beijing, China} % Location
    {Mar. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led team in developing FLT3-ITD NGS detection method for hematological tumors, achieving quantitative results stably consistent with gold standard capillary electrophoresis, meeting clinical application standards}
        \item {Led bioinformatics work for hematological tumor IVD R\&D, ensuring on-time project milestones and providing technical support for product registration}
      \end{cvitems}
    }\\

%---------------------------------------------------------
  \cventry
    {Hematological Tumor Project Bioinformatics Engineer} % Job title
    {Annoroad Gene Technology (Beijing) Co., Ltd.} % Organization
    {Beijing, China} % Location
    {Jul. 2015 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for end-to-end bioinformatics analysis of clinical commercial testing projects for hematological tumors, ensuring accuracy and timeliness of results to support clinical diagnostic decisions}
        \item {Independently developed a fully automated monitoring and operation platform, achieving error-free operation of clinical commercial testing for hematological tumors, improving reliability and efficiency of testing services}
      \end{cvitems}
    }\\



%---------------------------------------------------------
\end{cventries}
