%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Value Statement}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
In the field of bioinformatics, professionals with both deep industry practical experience and systematic academic training are extremely scarce. I have developed a unique competitive advantage combining "4 years of industry practice + doctoral academic research."

During my 4 years in industry, I grew from a Bioinformatics Engineer to a Bioinformatics Director, experiencing the complete process of technology implementation, team management, and project coordination. While serving as Director at Shenzhen AngelGen Technology Co., Ltd., I led the construction of a fully automated genetic disease detection platform, overseeing the entire chain from technical solution design to practical application, while also being responsible for the development of an integrated variant detection device, driving technology-to-product transformation. During my tenure as Project Leader at Beijing Genecast Biotechnology Co., Ltd., I led a team in developing an FLT3-ITD NGS detection method for hematological tumors, achieving quantitative results stably consistent with the gold standard capillary electrophoresis, directly supporting clinical application. These experiences have given me strong project implementation capabilities, team management skills, and technology commercialization mindset, enabling me to quickly identify industry needs and solve practical problems.

Subsequently, during my doctoral studies at The Chinese University of Hong Kong, I focused on bioinformatics algorithm development and computational biology research, participating in the development of multiple core research projects including BALEEN, FIN, and TAPE. Among these, the TAPE project results were published in Nature Communications (IF: 15.7), and provided key technical support for a 2022 Hong Kong RGC GRF approved project and a 2024 "1+1+1" Joint Fund approved project. My doctoral training further solidified my research innovation capabilities, enabling me to transform problems discovered in industry practice into academic research directions, and then feed industrial development through research achievements, forming a "practice-research-commercialization" closed loop.


% \begin{cvitems} % Description(s)
%     \item {Practical capabilities supporting Hainan's healthcare industry development: Hainan is vigorously developing healthcare, genetic testing, and other industries, while I possess rich technology development and project implementation experience in hematological tumor detection, genetic disease detection, and other fields: I have developed fully automated monitoring and operation platforms to ensure error-free operation of clinical commercial testing for hematological tumors, participated in hematological tumor IVD R\&D, and hold 5 bioinformatics detection-related patents (such as "A Method, Device, and Storage Medium for Detecting Copy Number Variations," "A Device for Detecting Somatic Mutations Related to Blood Diseases," etc.), capable of directly providing technical support to local Hainan medical institutions and genetic technology enterprises, promoting clinical testing technology upgrades, and assisting Hainan's healthcare industry in high-quality development.}
%     \item {Management potential meeting high-level talent team construction requirements: Hainan's high-level talent introduction policy, whether the "Talent from All Directions" excellent talent team funding or Hainan Normal University's research team support requirements, emphasizes talent's team building and management capabilities. I have led teams to complete core projects such as genetic disease detection platform construction and hematological tumor detection method R\&D, possessing experience in building efficient research and technology teams, able to integrate resources according to local Hainan needs, recruit and train young researchers, promote rapid team combat effectiveness formation, align with the policy's support orientation for team building, and contribute to Hainan's bioinformatics talent echelon construction.}
%     \item {If successfully selected as a high-level talent in Hainan, I will fully leverage my "practice + research" advantage: at the industrial level, connect with Hainan healthcare enterprises and medical institution needs, promote localized implementation of bioinformatics detection technologies, assist Hainan in building genetic testing and precision medicine industrial clusters; at the research level, rely on platforms such as Hainan Normal University to build bioinformatics research teams, conduct research around Hainan's characteristic fields such as tropical disease detection and marine organism genetic analysis, strive for approval of "South China Sea" talent-related projects, enhance Hainan's academic influence in bioinformatics; simultaneously, actively participate in talent training, integrate industry practical experience into teaching, train bioinformatics talents with both technical capabilities and practical thinking for Hainan, achieve deep integration of personal development and Hainan's construction, and contribute professional strength to Hainan Free Trade Port construction.}
% \end{cvitems}


\end{cvparagraph}
